\songtitle{Crown Him With Many Crowns}
\by{Matthew Bridges, 1852}
\comment{Rev. 19:12, 5:6, John 20:27}

\verse {
  \chord{D}Crown Him with \chord{Bm}many \chord{G}crowns,\\
  The \chord{D}Lamb up\chord{G}on \chord{(D)}His t\chord{A}hrone;\\
  Hark! \chord{D}how the \chord{Bm}heav'nly \chord{E}anthem \chord{A}drowns\\
  \chord{(D)}All \chord{A}music \chord{Esus}but \chord{E}its \chord{A}own. \chord{A7}\\
  A\chord{D}wake my soul and \chord{G}sing\\
  Of \chord{E}Him who died for \chord{A}thee,\\
  \chord{A7}And \chord{D}hail Him \chord{G}as \chord{D}thy \chord{Em}matchless \chord{D}King\\
  Through \chord{G}all e\chord{A}terni\chord{D}ty.
}

\verse {
  \chord{D}Crown Him the \chord{Bm}Son of \chord{G}God,\\
  Be\chord{D}fore the \chord{G}worlds \chord{(D)}be-\chord{A}gan;\\
  And \chord{D}ye who \chord{Bm}tread where \chord{E}He hath \chord{A}trod,\\
  \chord{(D)}Crown \chord{A}Him the \chord{Esus}Son \chord{E}of \chord{A}Man. \chord{A7}\\
  Who \chord{D}every grief hath \chord{G}known\\
  That \chord{E}wrings the human \chord{A}breast,\\
  \chord{A7}And \chord{D}takes and \chord{G}bears \chord{D}it \chord{Em}for His \chord{D}own\\
  That \chord{G}all in \chord{A}Him might \chord{D}rest.
}

\verse {
  \chord{D}Crown Him the \chord{Bm}Lord of \chord{G}life,\\
  Who \chord{D}triumphed \chord{G}o'er \chord{(D)}the \chord{A}grave,\\
  And \chord{D}rose vic\chord{Bm}torious \chord{E}in the \chord{A}strife\\
  \chord{(D)}For \chord{A}those He \chord{Esus}came \chord{E}to \chord{A}save; \chord{A7}\\
  His \chord{D}glories now we \chord{G}sing,\\
  Who \chord{E}died and rose on \chord{A}high,\\
  \chord{A7}Who \chord{D}died e\chord{G}ter\chord{D}nal \chord{Em}life to \chord{D}bring,\\
  And \chord{G}lives, that \chord{A}death may \chord{D}die.
}

\verse {
  \chord{D}Crown Him the \chord{Bm}Lord of \chord{G}peace,\\
  Whose \chord{D}pow'r a \chord{G}scep\chord{(D)}ter s\chord{A}ways\\
  From \chord{D}pole to \chord{Bm}pole that \chord{E}wars may \chord{A}cease,\\
  \chord{(D)}And \chord{A}all be \chord{Esus}prayer \chord{E}and \chord{A}praise: \chord{A7}\\
  His \chord{D}reign shall know no \chord{G}end,\\
  And \chord{E}round His pierced \chord{A}feet\\
  \chord{A7}Fair \chord{D}flowers of \chord{G}pa\chord{D}ra\chord{Em}dise ex\chord{D}tend\\
  Their \chord{G}fragrance \chord{A}ever \chord{D}sweet.
}

\verse {
  \chord{D}Crown Him the \chord{Bm}Lord of \chord{G}love;\\
  Be\chord{D}hold His \chord{G}hands \chord{(D)}and \chord{A}side,\\
  Those \chord{D}wounds yet \chord{Bm}visi\chord{E}ble a\chord{A}bove,\\
  \chord{(D)}In \hspace{2mm}\chord{A}beauty \chord{Esus}glor\hspace{1mm}-\hspace{1mm}\chord{E}i\hspace{1mm}-\hspace{1mm}\chord{A}fied:\chord{A7}\\
  All \chord{D}hail, Redeemer \chord{G}hail!\\
  For \chord{E}Thou has died for \chord{A}me:\\
  \chord{A7}Thy \chord{D}praise and \chord{G}glo\chord{D}ry \chord{Em}shall not \chord{D}fail\\
  Through\chord{G}out e\chord{A}terni\chord{D}ty.
}
